Bayesian Hyper-Heuristics

### 2023-01-22 article/sections/01-introduction.tex
✨ (article): Heuristics section done

Many different heuristics have been developed and used to train \acp{ANN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \acs{ANN} is required in order to yield optimal results. This process is often non-trivial and could be a time-consuming exercise.  Selection of the best heuristic to train \acp{ANN}, is often problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.

A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process. This approach focuses on the hybridisation of learning paradigms. One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}. These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce. \citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

@@

The remainder of this article is structured as follows: Section~\ref{sec:anns} provides background information on \acp{ANN}. Section~\ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}. Section~\ref{sec:hhs} presents background information on \acp{HH} and \index{meta-learning}meta-learning. Section~\ref{sec:probability} presents background information on probability theory. Section~\ref{sec:bhh} presents the developed \Acs{BHH}. Section~\ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment. Section~\ref{sec:results} provides and discusses the results of the empirical study. Section~\ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings made throughout the research process.

>>>>

Many different heuristics have been developed and used to train \acp{ANN}  \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train the \acs{ANN} is required in order to yield optimal results. This process is often non-trivial and could be a time-consuming exercise.  Selection of the best heuristic to train \acp{ANN}, is often problem specific  \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.

A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process. This approach focuses on the hybridisation of learning paradigms. One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem  \cite{ref:burke:2013}. These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce. \citeauthor{ref:nel:2021}  \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

@@

The remainder of this article is structured as follows: Section  \ref{sec:anns} provides background information on \acp{ANN}. Section  \ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}. Section  \ref{sec:hhs} presents background information on \acp{HH} and \index{meta-learning}meta-learning. Section  \ref{sec:probability} presents background information on probability theory. Section  \ref{sec:bhh} presents the developed \Acs{BHH}. Section  \ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment. Section  \ref{sec:results} provides and discusses the results of the empirical study. Section  \ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings made throughout the research process.

### 2023-01-22 article/sections/02-artificial-neural-networks.tex
✨ (article): Heuristics section done

\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain~\cite{ref:engelbrecht:2007}. \acp{ANN} have been successfully applied to a range of problem classes.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN}. These include classification~\cite{ref:khan:2001}, pattern matching~\cite{ref:cannady:1998, ref:kumar:1994}, pattern completion~\cite{ref:dayhoff:2001}, optimisation~\cite{ref:specht:1991} and data mining~\cite{ref:singh:2009}.

@@

\Acp{AN} provide the fundamental building blocks for \acp{ANN}. The \acs{AN} implements a non-linear mapping from $\mathbb{R}^{I}$ to $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the problem being solved ~\cite{ref:engelbrecht:2007}. $I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space. The \acs{AN} implements various components and is illustrated in Figure~\ref{fig:artificial_neuron}.

@@

Each of the components of the \acs{AN}, presented in Figure~\ref{fig:artificial_neuron}, is inspired by some element of the \acs{BN}. The input ($\boldsymbol{x}$) models the activations received from the pre-synaptic neuron. The weights ($\boldsymbol{v}$), model the \index{synapse}synapses and connection strengths. The \index{net input signal}net input signal ($net$) models the net resulting activations from all connected pre-synaptic neurons. The biases ($\theta$), model a mechanism introduced to influence the strength of the activation (output signal) of the \acs{AN}. The activation function ($f$) models the action potential of the \acs{BN} and is based on the net input signal. Finally, the output ($\boldsymbol{y}$) models the activation by the post-synaptic neuron.

@@

Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN} referred to as an \acf{ANN}. The architecture of the \acs{ANN} refers to the way in which \acp{AN} are organised. \acp{ANN} can be organised in layers where a single layer can contain multiple \acp{AN}. Generally, each layer makes use of the same \index{activation function}activation function. Output from one layer is propagated as input to the next layer. The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other. There are many different topologies~\cite{ref:miikkulainen:2010}.

This research focuses on a particular type of \acs{ANN}, referred to as \acp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed~\cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles~\cite{ref:zell:1994}.

In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes. An illustration of a \acs{FFNN} is given in Figure~\ref{fig:ffnn}.

@@

In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\boldsymbol{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\boldsymbol{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.

@@

\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution~\cite{ref:geron:2017}. The \acs{FFNN} learns the mapping function from the input to the target output~\cite{ref:brownlee:2016}.

>>>>

\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain  \cite{ref:engelbrecht:2007}. \acp{ANN} have been successfully applied to a range of problem classes.  \citeauthor{ref:engelbrecht:2007}  \cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN}. These include classification  \cite{ref:khan:2001}, pattern matching  \cite{ref:cannady:1998, ref:kumar:1994}, pattern completion  \cite{ref:dayhoff:2001}, optimisation  \cite{ref:specht:1991} and data mining  \cite{ref:singh:2009}. \Acp{AN} provide the fundamental building blocks for \acp{ANN}.

@@

The \acs{AN} implements a non-linear mapping from some $I$-dimensional, real-numbered input space to some $T$-dimensional, real-numbered output space. The output space is usually in the ranges $[0,1]$ or $[-1,1]$, depending on the problem being solved \cite{ref:engelbrecht:2007}. The \acs{AN} implements various components and is illustrated in Figure  \ref{fig:artificial_neuron}.

@@

Each of the components of the \acs{AN}, presented in Figure  \ref{fig:artificial_neuron}, is inspired by some element of the \acs{BN}. The input ($\boldsymbol{x}$) models the activations received from the pre-synaptic neuron. The weights ($\boldsymbol{v}$), model the \index{synapse}synapses and connection strengths. The \index{net input signal}net input signal ($net$) models the net resulting activations from all connected pre-synaptic neurons. The biases ($\theta$), model a mechanism introduced to influence the strength of the activation (output signal) of the \acs{AN}. The activation function ($f$) models the action potential of the \acs{BN} and is based on the net input signal. Finally, the output ($\boldsymbol{y}$) models the activation by the post-synaptic neuron.

@@

Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN} referred to as an \acf{ANN}. The architecture of the \acs{ANN} refers to the way in which \acp{AN} are organised. \acp{ANN} can be organised in layers where a single layer can contain multiple \acp{AN}. Generally, each layer makes use of the same \index{activation function}activation function. Output from one layer is propagated as input to the next layer. The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other. There are many different topologies  \cite{ref:miikkulainen:2010}.

This research focuses on a particular type of \acs{ANN}, referred to as \acp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed  \cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles  \cite{ref:zell:1994}.

In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes. An illustration of a \acs{FFNN} is given in Figure  \ref{fig:ffnn}.

@@

In Figure  \ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\boldsymbol{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\boldsymbol{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.

@@

\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution  \cite{ref:geron:2017}. The \acs{FFNN} learns the mapping function from the input to the target output  \cite{ref:brownlee:2016}.
